\bf Title here

### 2020-07-29 paper/paper.Rmd
modifying 4.1 done

[I would expand this section more as the core contribution. ppp]

@@

<!-- Visualisation has been widely used for exploring and understanding data. Presenting information in a graphical manner often allows people to see information they would otherwise not seen. -->

Random search methods has a black-box mechanism and focuses solely on finding the global maximum point, while the projection pursuit explores the data with an aim to discover the potential underlying structure and thus is interested in how the algorithm finds its maximum. This motivates us **to develop a visual diagnostic system for exploring the optimisation searching path**.

The necessity of developing such a system rather than simply producing different diagnostic plots is because the diagnostics of each variable requires a different function and these functions can't be scaled to other problems. Thus we want to establish a set of rules that can generalise the diagnostic of iterative algorithms.

The idea of generalising all the diagnostic plots under one framework is inspired by the concept of *grammar of graphic*[@wickham2010layered], which powers the primary graphical system in R, ggplot2 [@ggplot2]. In grammar of graphic, plots are not defined by its appearance (i.e. boxplot, histogram, scatter plot etc) but by "stacked layers". By this design, ggplot doesn't need to develop a gazillion of functions that each produces a different type of plot. Instead, it aesthetically maps the variables to the geometric objects and builds the plot through different layers.

@@

Tidy data, as introduced in [@wickham2014tidy], has three criteria:  1) each observation forms a row, 2) each variable forms a column and 3) each type of observational unit forms a table. The adoption of tidy data makes it easier for data wrangling and visualisation. For our visual diagnostics, global object is a such data construction with key components in optimisation algorithms and is designed for making diagnostic plots easier. In the optimisation algorithms for projection pursuit, two key elements are the projection basis: $\mathbf{A}$ and the index value: $I$. State: $S$ labels the observation with detailed stage of searching or interpolation.

>>>>

@@

We can see from Figure \ref{tour-path} that only the data projected using the outputted bases and interpolated bases are animated by tour; none of the searching bases are presented in teh tour animation. The optimisation algorithms in projection pursuit, although has been demonstrated to find the global maximum in various literature we referred above, focuses solely on finding the global maximum and remains as black-box machanisms. There has been fewer tools available to explore how each algorithm iteratively finds its maximum and compare how different algorithms searches the parameter space. Visualisation has been widely used for exploring and understanding data. Presenting information in a graphical manner often allows people to see information they would otherwise not seen. This motivates us **to develop a visual framework to diagnose optimisation algorithms in projection pursuit with a aim to understand and compare different existing algorithms.** This study is meaningful because **as more complex index functions are proposed, only an appropriate optimisation algorithm allows us to find the projection basis that presents interesting underlying structure in the data**.

The idea of generalised framwork for diagnostic plots is inspired by the concept of grammar of graphic [@wickham2010layered], which powers the primary graphical system in R, ggplot2 [@ggplot2]. In grammar of graphic, plots are not defined by its appearance (i.e. boxplot, histogram, scatter plot etc) but by "stacked layers". Using this design, ggplot doesn't have to develop a gazillion of functions that each produces a different type of plot from a different data structure. Instead, it aesthetically maps variables (and its statistical transformation) in a dataset to different geometric objects (points, lines, box-and-whisker etc) and builds the plot through overlaying different layers. There are different ways to represent the same data in rectangular form. Certain cleaning steps are needed, before using ggplot2, to bring the data into a tidy data format [@wickham2014tidy] where 1) each observation forms a row; 2) each variable forms a column and 3) each type of observational unit forms a table. In a tidy format, data wrangling and visualisation are greatly simplified.

Hence the study **contributes to set up a tidy data structure for collecting observations from optimisation algorithms and prescribe a set of rules for generalising diagnostic plots for optimisation algorithms, specifically those used for projection pursuit.**

@@

 For our visual diagnostics, global object is a such data construction with key components in optimisation algorithms and is designed for making diagnostic plots easier. In the optimisation algorithms for projection pursuit, two key elements are the projection basis: $\mathbf{A}$ and the index value: $I$. State: $S$ labels the observation with detailed stage of searching or interpolation.

### 2020-07-29 paper/paper.tex
modifying 4.1 done

{[}I would expand this section more as the core contribution. ppp{]}

@@

Random search methods has a black-box mechanism and focuses solely on
finding the global maximum point, while the projection pursuit explores
the data with an aim to discover the potential underlying structure and
thus is interested in how the algorithm finds its maximum. This
motivates us \textbf{to develop a visual diagnostic system for exploring
the optimisation searching path}.

The necessity of developing such a system rather than simply producing
different diagnostic plots is because the diagnostics of each variable
requires a different function and these functions can't be scaled to
other problems. Thus we want to establish a set of rules that can
generalise the diagnostic of iterative algorithms.

The idea of generalising all the diagnostic plots under one framework is
inspired by the concept of \emph{grammar of
graphic}\citep{wickham2010layered}, which powers the primary graphical
system in R, ggplot2 \citep{ggplot2}. In grammar of graphic, plots are
not defined by its appearance (i.e.~boxplot, histogram, scatter plot
etc) but by ``stacked layers''. By this design, ggplot doesn't need to
develop a gazillion of functions that each produces a different type of
plot. Instead, it aesthetically maps the variables to the geometric
objects and builds the plot through different layers.

@@

Tidy data, as introduced in \citep{wickham2014tidy}, has three criteria:
1) each observation forms a row, 2) each variable forms a column and 3)
each type of observational unit forms a table. The adoption of tidy data
makes it easier for data wrangling and visualisation. For our visual
diagnostics, global object is a such data construction with key
components in optimisation algorithms and is designed for making
diagnostic plots easier. In the optimisation algorithms for projection
pursuit, two key elements are the projection basis: \(\mathbf{A}\) and
the index value: \(I\). State: \(S\) labels the observation with
detailed stage of searching or interpolation.

>>>>

@@

We can see from Figure \ref{tour-path} that only the data projected
using the outputted bases and interpolated bases are animated by tour;
none of the searching bases are presented in teh tour animation. The
optimisation algorithms in projection pursuit, although has been
demonstrated to find the global maximum in various literature we
referred above, focuses solely on finding the global maximum and remains
as black-box machanisms. There has been fewer tools available to explore
how each algorithm iteratively finds its maximum and compare how
different algorithms searches the parameter space. Visualisation has
been widely used for exploring and understanding data. Presenting
information in a graphical manner often allows people to see information
they would otherwise not seen. This motivates us \textbf{to develop a
visual framework to diagnose optimisation algorithms in projection
pursuit with a aim to understand and compare different existing
algorithms.} This study is meaningful because \textbf{as more complex
index functions are proposed, only an appropriate optimisation algorithm
allows us to find the projection basis that presents interesting
underlying structure in the data}.

The idea of generalised framwork for diagnostic plots is inspired by the
concept of grammar of graphic \citep{wickham2010layered}, which powers
the primary graphical system in R, ggplot2 \citep{ggplot2}. In grammar
of graphic, plots are not defined by its appearance (i.e.~boxplot,
histogram, scatter plot etc) but by ``stacked layers''. Using this
design, ggplot doesn't have to develop a gazillion of functions that
each produces a different type of plot from a different data structure.
Instead, it aesthetically maps variables (and its statistical
transformation) in a dataset to different geometric objects (points,
lines, box-and-whisker etc) and builds the plot through overlaying
different layers. There are different ways to represent the same data in
rectangular form. Certain cleaning steps are needed, before using
ggplot2, to bring the data into a tidy data format
\citep{wickham2014tidy} where 1) each observation forms a row; 2) each
variable forms a column and 3) each type of observational unit forms a
table. In a tidy format, data wrangling and visualisation are greatly
simplified.

Hence the study \textbf{contributes to set up a tidy data structure for
collecting observations from optimisation algorithms and prescribe a set
of rules for generalising diagnostic plots for optimisation algorithms,
specifically those used for projection pursuit.}

@@

For our visual diagnostics, global object is a such data construction
with key components in optimisation algorithms and is designed for
making diagnostic plots easier. In the optimisation algorithms for
projection pursuit, two key elements are the projection basis:
\(\mathbf{A}\) and the index value: \(I\). State: \(S\) labels the
observation with detailed stage of searching or interpolation.
